% LaTeX CV
% ------------
% Author: Stephen Paul Ierodiaconou, 2011

\documentclass[10pt]{article}
% Depends on:
\usepackage{ifthen}
\usepackage{geometry}
\usepackage[usenames,dvipsnames]{color}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{enumitem}
\usepackage{setspace}

% Optionally remove page numbers:
%\thispagestyle{empty}\pagestyle{empty}

% No indent and increased paragraph spacing
\setlength{\parindent}{0pt}

% Configure margins:
\geometry{top=2.0cm,bottom=2.0cm,left=3.0cm,right=3.0cm}

% Commands
% - \cvtitle{Name}{ColorForName}{LiteralsOrRightText}{SpaceBelow} - Creates the CV title
\newcommand{\cvtitle}[4] {%
	{\LARGE\color{#2}\textsc{#1}}\hspace{\stretch{3}}{\large \textbf{#3}}\\[#4]}

% - \positionedbox{TextSide}{Width}{TextContent} - Creates a box of given width with text aligned as specified by 'TextSide' of given width. Note if you use box sizes which are less that the width of the page they can wrap together , ie 2 boxes of size 0.5\textwidth will sit side by side
\newcommand{\positionedbox}[3]{%
	\begin{minipage}{#2}
		\begin{flush#1}
			#3
		\end{flush#1}
	\end{minipage}}

% - \information{pieceofinfo}{pic/rightpic/space/none}{character} - Displays a piece of information pre/post-fixed with a 'character' symbol (pic), or leading space (space) or nothing (none).
% characters: phone = \Telefon, letter = \Letter, email = \MVAt, URL = \Flatsteel, twitter = $\mathcal{T}$
% NOTE: at the moment if you specify 'none' for the type, you still should put a non breaking space for 'character'
\newcommand{\information}[3]{
		\ifthenelse{\equal{#2}{pic}}
			{#3~ }
			{\ifthenelse{\equal{#2}{space}}
				{~ ~ }
				{}
			}
		#1\ifthenelse{\equal{#2}{rightpic}}
			{~ #3}
			{}
		}

% \cvheaderseperator{a}{b}{c}: Creates a horizontal rule separator where 'a' is the thickness, 'b' is the spacing above and 'c' is the spacing below.
\newcommand{\cvheaderseperator}[3]{\\[#2]\rule{\linewidth}{#1}\\[#3]}

% \cvskill{skill}{type}: Creates a 'skill' bullet. 'skill' is the actual skill text and 'type' is one of 'full', 'semi' or 'none' to indicate whether a full, half-full or empty bullet circle should be used. 
\newcommand{\cvskill}[2]{\hspace{4mm}%
	\ifthenelse{\equal{#2}{full}}%
		{\CIRCLE~ }%
		%else%
		{\ifthenelse{\equal{#2}{semi}}%
			{\LEFTcircle ~ }%
			{\Circle ~ }}#1\\}

% \cvsectiontitle{title}: Creates a section with the given title.
\newcommand{\cvsectiontitle}[1]{%
	\rule{\linewidth}{0.2mm}\\%
		{\large\indent\textsc{#1}}\\%
	\\[-6mm]\rule{\linewidth}{0.2mm}\\[2mm]%
	}

% \cvpub{Authors}{Title}{Date}{Journal/Conference}{Pages}: Create a publication entry
\newcommand{\cvpub}[5]{#1. (#3) ``#2'' \emph{#4}, pages #5} 

% \cvcompany{Name}{Date}: A new company in the experience section
\newcommand{\cvcompany}[2]{\textbf{#1}\hspace{\stretch{3}}{(#2)}}

% \cvsublevel{Text}: Create an indented item list
\newcommand{\cvsublevel}[1]{\begin{itemize}[leftmargin=0.5cm] #1\end{itemize}}

% \cvsubbullet{Text}: Create a buller in the sub level
\newcommand{\cvsubbullet}[1]{\vspace{-1mm}\item #1}

% Modify List enviroment
\renewcommand{\labelitemi}{\RIGHTarrow}
\renewcommand{\labelitemii}{$\bullet$}
\renewcommand{\labelitemiii}{\RIGHTarrow}
\renewcommand{\labelitemiv}{\RIGHTarrow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                    Content                                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\pagenumbering{gobble}
\cvtitle{Jeffrey Brock}{BrickRed}{}{0.5cm}
\positionedbox{left}{0.7\textwidth}{%
	\information{801 510 7877}{pic}{\Telefon}\\%
	\information{boccobrock@gmail.com}{pic}{\MVAt}\\%
    \information{github.com/boccobrock}{pic}{\texttt{\{\}}}\\%
}
\\[0.4cm]
\cvsectiontitle{Education}
\vspace{-0.8cm} % NOTE: There are spacing issues, not sure why, fix them with some vspace
\begin{itemize}[leftmargin=0.5cm]
\item \cvcompany{University of Utah - Bachelor of Computer Science}{2008 - 2015}
\item \cvcompany{West High School}{2002 - 2008}
\end{itemize}

% Skill set
\cvsectiontitle{Skills}
Languages and associated frameworks that I have experience working with:
\\[0.4cm]
\positionedbox{left}{0.5\textwidth}{
\cvskill{Java - Spring, Hibernate, Selenium}{full}
\cvskill{C++ - Boost, Ogre, Windows API}{full}
\cvskill{C - ffmpeg, EFI}{full}
\cvskill{C\# - Webforms, ASP}{full}
\cvskill{CSS - Bootstrap, Pure}{full}
}
\positionedbox{left}{0.4\textwidth}{
\cvskill{Javascript - AngularJS, Node.js}{full}
\cvskill{Ruby - Rails}{full}
\cvskill{PHP - Zend}{full}
\cvskill{DB - MySQL, Mongo, MSSQL}{full}
\cvskill{Design - Photoshop, Gimp}{full}
}
\\[0.4cm]
\textbf{Other Tools} Proficient with SVN and Git, and an expert with Jira and other Atlassian tools.
\\Experienced with many Linux distributions, as well as Windows and OSX.
\\Comfortable working with a team of developers and good at communicating with others.
\\[0.2cm]
\textbf{Natural Languages} \emph{Native}: English, \emph{Fluent}: Portuguese

% Work experience. Education can be a similar block
\cvsectiontitle{Experience}
\vspace{-0.8cm} % NOTE: There are spacing issues, not sure why, fix them with some vspace
\begin{itemize}[leftmargin=0.5cm]
\item \cvcompany{Orchid Event Solutions - Software Developer}{Oct 2014 - Ongoing}\cvsublevel{%
    \cvsubbullet{Maintenance and developing new features for a core framework in ASP, both Webforms and MVC. This framework is used for registration sites for large conventions, using features I created such as localization.}
    \cvsubbullet{Used tools such as HTML5, CSS with bootstrap, JMeter load testing and JQuery for Javascript. These sites were designed for mobile web as well as desktop use. Also used TFS and Microsoft SQL working with a small development team.}%
	}
\item \cvcompany{Xi3 Corporation - Software Developer}{Oct 2013 - Oct 2014}\cvsublevel{%
	\cvsubbullet{Implemented update system with C++ sockets to a Node.js server. Used HTML and CSS with JQuery to create sites for admin functions. Implemented IPC with sockets, and built a 2D and 3D windows application with many integrations with Windows. Set up a build server, Git workflow, test case framework, use of a Jira and other development practices.}%
	}
\item \cvcompany{Christopherson Business Travel - Tester and Software Developer}{Aug 2011 - Oct 2013}\cvsublevel{%
	\cvsubbullet{Responsible for developing new tools from the back end up to the front end. Used HTML5, CSS3 and JQuery to create web UI interfaces. Made modifications to the MySQL database, and helped develop the backend Java web service that used Hibernate and Spring.  Made front end tools with PHP and Javascript. Wrote Selenium tests to test site functionality, and use JMeter to load test.}%
	}
\end{itemize}

\cvsectiontitle{About Me}
I like doing all kinds of projects and find programming very enjoyable. I've been coding since High School, and I have experience with a wide range of languages and frameworks.
\\[0.3cm]
I also do my own personal projects when time permits. My code can be found on github at the address in my info section.
\end{document}
